---
title: SSA Vic & Tas Councils
---


```{r setup, include = FALSE}
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

council <- read_csv("data/councils.csv")
```

## Current

```{r current, results = "asis"}
df <- council %>% 
  filter(Year == year(Sys.Date()))

if(nrow(df)==0) {
  df <- council %>% 
    filter(Year == year(Sys.Date()) - 1)
}

cat(paste(paste("*",  c(df$President, 
        df$Past.Vice.President., 
        df$Secretary, 
        df$Treasurer,
        df$Other.members.of.council %>% 
          str_split(",") %>% 
          .[[1]] %>% 
          str_trim())), collapse = "\n"))
```


## Past 


```{r past}
council %>% 
  filter(Year < year(Sys.Date())) %>% 
  # remove titles
  mutate(across(President:Treasurer,
                ~str_replace(.x, "(^Prof|^Assoc Prof|^Dr[.]?) ", ""))) %>% 
  mutate(Other.members.of.council = str_replace_all(Other.members.of.council, "(Dr|Miss|Ms|Prof) ", " ")) %>% 
  arrange(desc(Year)) %>% 
  knitr::kable(col.names = c("Year", "President", "Vice President", "Secretary", "Treasurer", "Other members of council")) %>% 
  kableExtra::kable_classic()
```


\*According to the original Victorian Branch Constitution, the Branch
President had to be elected each year. An individual could serve as the
Branch President for a maximum of two years in succession, then as the
Immediate Past President for one or two years, as the circumstances
dictated. The Past President was an automatic (unelected) member of
Branch Council. At the AGM in March 1999, the membership voted to change
the Constitution. In years when the Past President retired at the AGM in
March, an incoming President would be voted in for a four year-term:
Vice-President for one year, President for the next two years, and then
Past President for one year. The motivation was that the Vice-President
then had a year to prepare for office. Before 1999 the new President had
been thrust suddenly into the job. Thus in column 3 of the table, the
Vice-President is listed in even years starting from 2000 (2002, 2004
and 2006 and so on).

In all other years, the Past President is listed (although in some years
the Past President could not fill the post, usually because he or she
had left Victoria).

☺ In 2002 the post of Branch SSAI Newsletter Correspondent was created
by Central Council. Each Branch nominated a member of Branch Council
to prepare regular Branch Reports for the SSAI Newsletter. The person
indicated by a ☺ is that year’s Victorian Branch Correspondent.

□ The Branch Council is supposed to have a Student Representative each
year. This has not always happened, and even when it has, the name of
the student representative has not always been explicitly noted in our
records. This information has therefore been omitted.

In 2020 the Young Statistician Representative position changed to the
Early Career and Student Statistician Representative (ECSS)
